Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Edit colors in violin plots for weibull fits to dispersal data

@@

 **NEXT** Instead of the violin plots, I should show the dispersal kernels created by each of these bootstrap replicates.   
 Also, seems like for simulations, we need to sample 5 individuals multiple times, or sample more than 5 individuals from each population. I like the second approach because it resembles just sampling more individuals in the field, increasing your sample size to get a better picture of nature.
 Also, edit colors in violin plots to show each individuals color, and only use the one that includes the population as well. Leave population in black. Change red lines and dot to black too.

>>>>

weib.boot %>% 
  ggplot(., aes(x = factor(indiv), y = est.shape, color = factor(indiv))) +
  geom_violin() +
  scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.1) +
  # geom_point(color = "grey", alpha = 0.5) +
  stat_summary(fun.data=mean_sdl, mult=1, 
                 geom="pointrange", color="black") +
  labs(title = "Shape") +
  theme_bw() -> p1
# p1

weib.boot %>% 
  ggplot(., aes(x = factor(indiv), y = est.scale, color = factor(indiv))) +
  geom_violin() +
  scale_color_manual(values = c("black", mycols)) +
  #geom_boxplot(width = 0.1) +
  # geom_point() +
  stat_summary(fun.data=mean_sdl, mult=1, 
                 geom="pointrange", color="black") +
  labs(title = "Scale") +
  theme_bw() -> p2

@@

 **NEXT** Instead of the violin plots, I should show the dispersal kernels created by each of these bootstrap replicates.   
 Also, seems like for simulations, we need to sample 5 individuals multiple times, or sample more than 5 individuals from each population. I like the second approach because it resembles just sampling more individuals in the field, increasing your sample size to get a better picture of nature.
